---
title: "Untitled"
author: "Jonas Gehrlein"
date: "20 maj 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
```
First load data from Data folder and calculate the density in each orthofoto
FOr mark 1

```{r}
field_1 <- read.csv("G:/P8_projekt/Projekter/Prik_pr_billede/polypoints_m2_1.csv", sep = ',', dec = '.',
                      header = TRUE)
field_1$density <- field_1$droppings/field_1$m2
mean(field_1$density)
mean(field_1$density)

```

Then resample with replacement 100 times.
This resampling is done with a sample size from 1 to 100% of the original dataset.

```{r}
N <- 100
mean_dens <- matrix(,nrow = N, ncol = 100)
for (t in 1:100){
  for (i in 1:N){
  dens<- sample(field_1$density, replace = TRUE, size = (t/100)*length(field_1$density))
  mean_dens[i,t] <- mean(dens)
  
  }}
gns <- rep(NA,100)
afv <- rep(NA,100)
confd <- rep(NA,100)
for (i in 1:100){
  gns[i] <- mean(mean_dens[,i])
  afv[i] <- sd(mean_dens[,i])
  confd[i] <- afv[i]/sqrt(100) * 1.96
}
gns
afv 
confd
mean_dens[,i]
```

# Gør det med BCa bootstrap
```{r}
#install.packages("bootBCa", repos="http://R-Forge.R-project.org")
library('bootBCa')


boot.resamp <- cbind.data.frame(rep(NA,100),rep(NA,100),rep(NA,100))
colnames(boot.resamp) <- c("mean","lowerCI","upperCI")
for (i in 1:100){
    boot <- BCa(mean_dens[,i],0.01,mean,
                   alpha = c(0.025, 0.975),M = 100, Mlimit = 2000000)
    boot <- cbind.data.frame(boot)
    
  boot.resamp$lowerCI[i] <- boot[4,]
  boot.resamp$upperCI[i] <- boot[5,]
  boot.resamp$mean[i] <- boot[3,]
}

boot.resamp
```

## Omregn til procenter (forsøg)
```{r}

boot.resamp_field_1 <- boot.resamp

boot.resamp_field_1$mean.std <- (boot.resamp_field_1$mean-0.76)*100
boot.resamp_field_1$lowerCI.std <- (boot.resamp_field_1$lowerCI-0.76)*100
boot.resamp_field_1$upperCI.std <- (boot.resamp_field_1$upperCI-0.76)*100
boot.resamp_field_1
```


Then a example of a plot

```{r}
par(mfrow = c(2,1))
par(oma=c(3.8,2,2.5,2))
par(mar=c(1.1,2.8,0.7,2))
perc_vec <- rep(1:100)
perc_vec

a <-plot(perc_vec,boot.resamp$mean, ylim = c(0.6,1.), xlim = c(0,100), ann=FALSE, xaxt="n")
arrows(perc_vec, boot.resamp$lowerCI, perc_vec,boot.resamp$upperCI, code = 3, angle = 90, length = 0.05)
abline(v=25, col="red", lwd=3, lty=2)

# Test field
#mtext("3a",at=3.6, side=1, outer=F, cex=1.3, padj = -12.4)
```

################################################################################
First load data from Data folder and calculate the density in each orthofoto
FOr mark 2

```{r}
field_2 <- read.csv("G:/P8_projekt/Projekter/Prik_pr_billede/polypoints_m2_2.csv", sep = ',', dec = '.',
                      header = TRUE)
#field_2$m2[field_2$m2 > 10] = 6.68
#quantile(field_2$m2)
field_2$density <- field_2$droppings/field_2$m2
mean(field_2$density)
#View(field_2)
mean(field_2$density)
median(field_2$density)

```

Then resample with replacement 100 times.
This resampling is done with a sample size from 1 to 100% of the original dataset.

```{r}
N <- 100

mean_dens <- matrix(,nrow = N, ncol = 100)
for (t in 1:100){
  for (i in 1:N){
  dens<- sample(field_2$density, replace = TRUE, size = (t/100)*length(field_2$density))
  mean_dens[i,t] <- mean(dens)
  
  }}
gns <- rep(NA,100)
afv <- rep(NA,100)
confd <- rep(NA,100)
for (i in 1:100){
  gns[i] <- mean(mean_dens[,i])
  afv[i] <- sd(mean_dens[,i])
  confd[i] <- afv[i]/sqrt(100) * 1.96
}
gns
afv 
confd
#View(mean_dens)
mean_dens[,1]

mean(mean_dens[,1])
var(mean_dens[,1])
sd(mean_dens[,1])/sqrt(100)*1.96
#plot(mean_dens[,1])
```

# Gør det med BCa bootstrap
```{r}
# install.packages("bootBCa", repos="http://R-Forge.R-project.org")
library('bootBCa')


boot.resamp <- cbind.data.frame(rep(NA,100),rep(NA,100),rep(NA,100))
colnames(boot.resamp) <- c("mean","lowerCI","upperCI")
for (i in 1:100){
    boot <- BCa(mean_dens[,i],0.01,mean,
                   alpha = c(0.025, 0.975),M = 100, Mlimit = 2000000)
    boot <- cbind.data.frame(boot)
    
  boot.resamp$lowerCI[i] <- boot[4,]
  boot.resamp$upperCI[i] <- boot[5,]
  boot.resamp$mean[i] <- boot[3,]
}

boot.resamp
```


## Omregn til procenter (forsøg)
```{r}

boot.resamp_field_2 <- boot.resamp

boot.resamp_field_2$mean.std <- (boot.resamp$mean-6.76)*100
boot.resamp_field_2$lowerCI.std <- (boot.resamp$lowerCI-6.76)*100
boot.resamp_field_2$upperCI.std <- (boot.resamp$upperCI-6.76)*100
head(boot.resamp_field_2)
```


Then a example of a plot

```{r}
perc_vec <- rep(1:100)
perc_vec

a <-plot(perc_vec,boot.resamp$mean, ylim = c(6.2,7.4), xlim = c(0,100),
         main="Field 2 Estimation of dropping densities by resampling", ann=FALSE)
arrows(perc_vec, boot.resamp$lowerCI, perc_vec,boot.resamp$upperCI, code = 3, angle = 90, length = 0.05)


mtext("Data resampled (%)",at=0.52, side=1, outer=T, cex=1.4, padj = 2)
mtext(expression(Mean ~ droppings ~ m^{-2}), at=0.5, side=2, outer=T, cex=1.4, padj = 0)
# mtext("Measured density by resampling", at=0.5, side=3, outer=T, cex=1.8, padj = 0)
abline(v=25, col="red", lwd=3, lty=2)

# Test field
#mtext("3b",at=3.6, side=1, outer=F, cex=1.3, padj = -12.4)

```

############## FOrsøg med standardisering

Then a example of a plot (standardiseret)

```{r}
par(mfrow = c(2,1))
par(oma=c(3.8,2,2.5,2))
par(mar=c(1.1,2.8,0.7,2))
perc_vec <- rep(1:100)
perc_vec

a <-plot(perc_vec,boot.resamp_field_1$mean.std, ylim = c(-20.1,20.1), xlim = c(0,100), ann=FALSE, xaxt="n",cex.axis=1.1,pch = 19,cex=.7)
arrows(perc_vec, boot.resamp_field_1$lowerCI.std, perc_vec,boot.resamp_field_1$upperCI.std, code = 3, angle = 90, length = 0.05)
abline(v=25, col="red", lwd=3, lty=2)

# Test field
#mtext("3a",at=3.6, side=1, outer=F, cex=1.3, padj = -12.4)
```


Then a example of a plot (standardiseret)

```{r}
perc_vec <- rep(1:100)
perc_vec

a <-plot(perc_vec,boot.resamp_field_2$mean.std, ylim = c(-60.1,60.1), xlim = c(0,100),
         main="Field 2 Estimation of dropping densities by resampling", ann=FALSE,cex.axis=1.1,pch = 19,cex=.7)
arrows(perc_vec, boot.resamp_field_2$lowerCI.std, perc_vec,boot.resamp_field_2$upperCI.std, code = 3, angle = 90, length = 0.05)


mtext("Data resampled (%)",at=0.52, side=1, outer=T, cex=1.6, padj = 2)
mtext(expression(Difference ~ 'in' ~ mean ~ droppings ~ m^{-2} ~ '(%)'), at=0.5, side=2, outer=T, cex=1.6, padj = 0)
# mtext("Measured density by resampling", at=0.5, side=3, outer=T, cex=1.8, padj = 0)
abline(v=25, col="red", lwd=3, lty=2)

# Test field
#mtext("3b",at=3.6, side=1, outer=F, cex=1.3, padj = -12.4)

```

